\documentclass[a4paper,9pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\Large \textbf{H.R. Johnson}} \\
      {\small Full-Stack Developer Relations Engineer in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\
      \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}}
\end{center}

\section{Summary}
{\small Experienced full-stack engineer with 10+ years in community management. Proficient in JavaScript, React, Node.js, and recently self-taught in Flutter and Dart. Passionate developer advocate, experienced in creating engaging content, hosting events, and collaborating cross-functionally. Seeking to leverage my expertise to enhance developer relations at FlutterFlow.}

\section{Skills}
\textbf{\small Languages {$\parallel$} \normalfont{JavaScript,
            TypeScript, SQL, LaTeX, Dart, Flutter}}

\textbf{\small Tools \& Technologies {$\parallel$} \normalfont{HTML, CSS, React, Redux, REST, Git, Express.js, Node.js, PostgreSQL, Prisma, Jest, JWT, bcrypt, Jira, HubSpot, FirstData, Apps Scripts, GitHub, VS Code, WSL, Kanban, Agile}}

\textbf{\small Content Creation {$\parallel$} \normalfont{Technical writing, blog posts, whitepapers, webinars}}

\section{Experience}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Produced engaging technical content including blogs, guides, and whitepapers.
      \item Used ChatGPT to draft and refine content, automated responses, and enhance customer experience.
      \item Planned VIP, CEO, and Influencer publishing opportunities and community
            events and webinars.
      \item Increased user engagement from 2\% to 7\% with
            strategic
            development.
      \item Designed and developed Apps Scripts for engagement and retention
            projects.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Managed cross-functional teams in community forums and customer
            support.
      \item Assisted with project management, product development and UX design.
      \item Improved retention 5\% by implementing user-generated content contests.
      \item Increased moderator productivity and satisfaction ratings from 61\%
            to
            96\%.
      \item Handled customer support issues and abuse reports.
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$}{ Student} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development
            bootcamp.
      \item Developed advanced engineering projects, including e-commerce and gaming applications.
      \item Led projects and implemented continuous integration testing and code reviews.
      \item Utilized Midjourney to create visual content for websites, technical content and engagement.\\
\end{itemize}

\textbf{University of Washington, Seattle, WA} \hfill
\textbf{2011}
\\
Bachelor of Arts in Anthropology \& Archaeology, Summa cum laude

\section{FullStack Academy Capstone Projects}

\subsection{Alley Cat: Retro Side-Scroller Game {$\parallel$}{
                  Project Manager
                  \& Developer}
      \hfill \textbf{June 2024}}
{\small Led a team of 4 developers in building a retro-feeling
      side-scroller game using vanilla JavaScript and HTML5 canvas.
      Implemented
      project management best practices. Configured continuous integration testing and
      performed
      code reviews. Code deployed at \href{https://github.com/Cherry-Stone-Studios/Alley-Cat-Game}{github.com/Cherry-Stone-Studios/Alley-Cat-Game}.}

\subsection{E-Commerce App: PokeDealers {$\parallel$}{ Developer}
      \hfill \textbf{May 2024}}
{\small Worked with 2 other developers on a full-stack e-commerce
      app to provide a user-friendly shopping experience. Utilized React, Express.js and Prisma for database management. Code located
      at \href{https://github.com/Charmelions/PokeDealer}{github.com/Charmelions/PokeDealer}.}

\end{document}