\documentclass[a4paper,9pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Set up hyperref package
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    citecolor=black,
    filecolor=black,
    menucolor=black,
    runcolor=black
}

% Reduce spacing between items
\setlist{nosep, noitemsep}

% Define custom section format
\titleformat{\section}{\small\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\small\bfseries}{}{0em}{}
\titleformat{\subsubsection}{\small}{}{0em}{}

% Remove section numbering
\setcounter{secnumdepth}{0}

% Reduce space after title rules
\titlespacing*{\section}{0pt}{1ex}{1ex}
\titlespacing*{\subsection}{0pt}{0.5ex}{0.5ex}

% Reduce paragraph spacing
\setlength{\parskip}{0pt}

\begin{document}

\begin{center}
    {\Large \textbf{H.R. Johnson}} \\
    \vspace{0.1em}
    Kazoo, Michigan \\
    \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \\
    \href{tel:360-951-0354}{360-951-0354} \\
    \href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity} \\

    \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\section{Summary}
\noindent
Community-driven full-stack engineer with experience building inclusive
communities. Builds applications and games in JavaScript and SQL. Voracious
learner, meticulous with details, and tenacious problem-solver.

\section{Skills}
\subsection{Languages}
JavaScript, SQL, TypeScript, LaTeX

\subsection{Tools \& Technologies}
HTML, CSS, React, Redux, REST, Git, Express.js, Node.js, PostgreSQL, Prisma,
Supertest, Jest, Prisma Mock, CORS, React Router, JWT, Morgan, bcrypt,
Confluence, Jira, HubSpot, FirstData, Apps Scripts, GitHub, VS Code, WSL,
Kanban, Agile

\section{Education}
\textbf{University of Washington, Seattle, WA} \hfill \textbf{2011} \\
Bachelor of Arts in Anthropology \& Archaeology, Summa cum laude

\section{Experience}

\subsection{Fullstack Academy, Remote} \hfill \textbf{Feb 2024 – June 2024}
\textbf{Senior Software Engineer}
\begin{itemize}[leftmargin=1em, itemsep=0pt, parsep=0pt]
    \item Top-ranking graduate of the online full-time full-stack web
          development bootcamp.
    \item Learned advanced HTML, CSS, and JavaScript implementation and
          methodologies; application development with React; database design with Prisma;
          API creation with Express.js and complete integration and unit testing with
          Jest.
    \item Worked in different teams to build 2 fully functional full-stack
          applications. Utilized pair and mob programming during both projects.
    \item Created an e-commerce app. Wrote code to import public API data into
          a new database. Deployed app to Netlify and database to Render.
    \item Developed a full retro-feeling side-scroller game with vanilla JS and
          \textless canvas\textgreater with a team of 4 in under 3 weeks. Deployed both
          app and database to Render.
    \item Acted as project manager while working on side-scroller game,
          implementing tickets, lanes, and pull-request best practices. Configured GitHub
          for continuous integration testing. Performed code reviews for the team.
\end{itemize}

\subsection{Community.co, Remote} \hfill \textbf{July 2019 – June 2023}
\textbf{Community Manager}
\begin{itemize}[leftmargin=1em, itemsep=0pt, parsep=0pt]
    \item Acted as the sole community strategist and manager for an
          executive-based community with a focus on increasing their engagement and reach
          through our development.
    \item Designed and coded Apps Scripts against hand-collected data to drive
          engagement and retention projects.
    \item Created KPI using qualitative and quantitative member data, and
          achieved desired growth goals over time.
    \item Managed VIP, CEO, and Influencer publishing through major US-based
          business publications, including Forbes.
    \item Outreach to the community increased activity from 2\% to 7\% during
          tenure.
    \item Planned and managed community events, activities, and programs.
    \item Primary trainer for all new team members in community tactics and
          reporting.
\end{itemize}

\subsection{Internet Brands, Remote} \hfill \textbf{July 2013 – July 2019}
\textbf{Community Manager}
\begin{itemize}[leftmargin=1em, itemsep=0pt, parsep=0pt]
    \item Engaged with the community to create a pipeline of bug reports and
          feature suggestions that fed into the product and engineering teams' output.
          This actionable feedback was driven by qualitative and quantitative user data.
    \item Simultaneously managed the community and customer service teams,
          moderation teams, and administered the community forums.
    \item Implemented new site rules, policies, and standard operating
          procedures to satisfy legal and business needs on an ongoing basis.
    \item Increased moderator productivity and customer satisfaction across our
          portfolio of websites from 61\% to 96\% over two years.
    \item Created and implemented user-generated content contests and events
          resulting in increased retention over my tenure.
    \item Managed all customer support issues requests and resolved all abuse
          reports in accordance with legal mandates.
\end{itemize}

\end{document}
