\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\LARGE \textbf{H.R. Johnson}} \\
      Full-Stack Engineer in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\
      \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}
\end{center}

\section{Summary}
Experienced full-stack developer proficient in JavaScript, React, Node.js, and
PostgreSQL. Skilled in building scalable web apps, RESTful APIs, and designing
databases. Committed to delivering user-friendly solutions through teamwork and
continuous learning, driven by a passion for innovative tech projects.

\section{Skills}
\textbf{Languages {$\parallel$} \normalfont{ JavaScript,
            TypeScript, SQL, LaTeX}}

\textbf{Tools \& Technologies {$\parallel$} \normalfont{ HTML, CSS, React,
            Redux, REST, Git, Express.js, Node.js, PostgreSQL,
            Prisma, Jest, JWT, bcrypt, Jira, HubSpot, FirstData, Apps Scripts,
            GitHub, VS Code, WSL, Kanban, Agile}}

\section{FullStack Academy Capstone Projects}
\subsection{E-Commerce App: PokeDealers {$\parallel$}{ Developer}
      \hfill \textbf{May 2024}}
{Worked with 2 other developers on a full-stack e-commerce
      application
      to provide a user-friendly
      online shopping experience for Pokemon. Utilized React for the
      front-end, Express.js for
      the back-end API, and Prisma for database management. Code located
      at \href{https://github.com/Charmelions/charmelions}{github.com/Charmelions/charmelions}.}

\subsection{Alley Cat: Retro Side-Scroller Game {$\parallel$}{
                  Project Manager
                  \& Developer}
      \hfill \textbf{June 2024}
}
{Led a team of 4 developers in building a retro-feeling
      side-scroller game using vanilla JavaScript and HTML5 canvas.
      Implemented
      project management best practices, including tickets, lanes, and
      pull-request
      workflows. Configured GitHub for continuous integration testing and
      performed
      code reviews for the team. Code deployed at \href{https://github.com/Cherry-Stone-Studios/Cherry-Stone-Studios}{github.com/Cherry-Stone-Studios/Cherry-Stone-Studios}.}

\section{Experience}

\subsection{Fullstack Academy, Remote {$\parallel$}{ Student} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development
            bootcamp.
      \item Learned advanced engineering through
            hands-on
            projects and coursework.
      \item Acted as project manager, implementing tickets, pull requests, and
            continuous integration testing using GitHub.
      \item Performed code reviews and pair programming sessions, contributing
            to a high-quality codebase.
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Designed and developed Apps Scripts for engagement and retention
            projects.
      \item Managed VIP, CEO, and Influencer publishing and community
            events.
      \item Increased community activity from 2\% to 7\% through
            strategic
            initiatives.
      \item Trained team members in community tactics and reporting.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Managed community forums, moderation teams, and customer
            support.
      \item Implemented user-generated content contests and improved
            retention strategies.
      \item Increased moderator productivity and satisfaction from 61\%
            to
            96\%.
      \item Handled customer support issues and abuse reports.
\end{itemize}

\section{Education}
\textbf{University of Washington, Seattle, WA} \hfill
\textbf{2011}
\\
Bachelor of Arts in Anthropology \& Archaeology, Summa cum laude

\end{document}