\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\LARGE \textbf{H.R. Johnson}} \\
      Community-Driven in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\

      \mbox{\href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \&

            \href{mailto:amazonxprincezz@yahoo.com}{amazonxprincezz@yahoo.com}}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}
\end{center}

\section{Summary }
\noindent
Experienced professional with 10+ years in customer service and community
management. Excellent communication and interpersonal skills, with a
commitment to excellence and attention to detail. Adherent to high standards
while working to understand, meet, and exceed guest expectations.

\section{Skills}
\textbf{Languages {$\parallel$} \normalfont{ French (Intermediate Proficiency),
            JavaScript, SQL}}

\textbf{Tools \& Technologies {$\parallel$} \normalfont{ Hootsuite, Canva,
            Zendesk, Jira, HubSpot CRM, Apps Scripts}}

\section{Experience}

\subsection{Air Zoo Aerospace \& Science Museum, Kalamazoo, MI {$\parallel$}{
                  Guest Experience Ambassador} \hfill
      \textbf{Aug 24 – Current}}
\begin{itemize}
      \item Guided guests through museum experience while operating from a
            stationary assignment.
      \item Engaged with guests, provide information about artifacts at the
            museum,
            and correctly answer guest questions.
      \item Helped manage flow of crowds, efficiently helping guests with needs
            and
            directing as needed.
      \item Ensured guest safety in various situations with various crowd
            sizes.
\end{itemize}

\subsection{Communitrix, Remote {$\parallel$}{ Founder} \hfill
      \textbf{Sep 2023 – Present}}
\begin{itemize}
      \item Drafted and implemented custom community plans for clients.
      \item Maintained client Shopify site and codebase for client's website.
      \item Created written and visial media content for client social media.
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Managed VIP, CEO, and Influencer publishing and community
            events.
      \item Increased community activity from 2\% to 7\% through
            strategic
            initiatives.
      \item Supervised and trained team members in community tactics and reporting.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Upsold \$500,000 worth of online memberships through direct communications.
      \item Managed cross-functional teams in community forum moderation and customer
            service.
      \item Assisted with project management, product development and social media content creation.
      \item Increased customer satisfaction from 61\%
            to
            96\%.
      \item Handled escalated customer support issues and abuse reports.
\end{itemize}

\subsection{ModSquad, Remote {$\parallel$}{ Social Media Strategist} \hfill
      \textbf{Aug 2010 – Feb
            2012}}
\begin{itemize}
\item Executed social media strategies pursuant to client requests and needs.
\item Provided concierge-level customer service and online moderation services.
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$} {Junior Developer} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development bootcamp.
      \item Learned advanced web engineering through
            hands-on projects and coursework.
\end{itemize}

\subsection{University of Washington, Seattle {$\parallel$}{ Bachelor of Arts
                  in Anthropology} \hfill
      \textbf{2011}}
\begin{itemize}
      \item Top-ranking graduate, Summa cum laude
      \item Focused on Archaeology, Anthropology, Oceanography, Geology
\end{itemize}

\end{document}