\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\LARGE \textbf{H.R. Johnson}} \\
      Community-Driven in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\
      \mbox{\href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \& \href{mailto:amazonxprincezz@yahoo.com}{amazonxprincezz@yahoo.com}}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}
\end{center}

\section{Summary}
\noindent
Experienced professional with 10+ years in customer service, moderation, with social media and community management. Skilled in creating social media content, blogs, guides, whitepapers, videos, webinars and technical documentation. Proven ability to translate complex concepts for diverse audiences and collaborate cross-functionally. Seeking to leverage my expertise for the ModSquad once again.

\section{Skills}
\textbf{Languages {$\parallel$} \normalfont{ French (Intermediate Proficiency), JavaScript, SQL}}

\textbf{Tools \& Technologies {$\parallel$} \normalfont{ Hootsuite, Canva, Zendesk, Jira, HubSpot CRM, HTML, CSS, Apps Scripts}}

\section{Experience}

\subsection{Communitrix, Remote {$\parallel$}{ Founder} \hfill
      \textbf{Sep 2023 – Present}}
\begin{itemize}
\item Obtained and maintained small but strong client base
\item Drafted and implemented custom community plans for clients
\item Maintained client codebases and updated websites with modern security
\item Created standard and milestone-based contracts for clients
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Designed and developed Apps Scripts for engagement and retention
            projects.
      \item Used ChatGPT to draft and refine content, automated responses, and enhance customer experience.
      \item Managed VIP, CEO, and Influencer publishing and community
            events.
      \item Increased community activity from 2\% to 7\% through
            strategic
            initiatives.
      \item Trained team members in community tactics and reporting.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Managed cross-functional teams in community forums and customer support.
      \item Assisted with project management, product development and UX design.
      \item Increased customer satisfaction from 61\%
            to
            96\%.
      \item Handled escalated customer support issues and abuse reports.
\end{itemize}

\subsection{ModSquad, Remote {$\parallel$}{ Moderator and Social Media Strategist} \hfill
      \textbf{Aug 2010 – Feb
            2012}}
\begin{itemize}
      \item Executed social media strategies pursuant to client requests and needs.
\item Created compelling content, tutorials and game guides, including in-game video content.
\item Provided concierge-level customer service and online moderation services
\item Engaged in regular in-game and online events, user-generated content contests, tournaments, and meetups.
\item Moderated a AAA MMO by assisting players with in-game concerns, bug reports, and account management.
\item Responded to trouble tickets with Zendesk customer service software.
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$} {Junior Developer} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development
            bootcamp.
      \item Learned advanced web engineering through
            hands-on
            projects and coursework.
      \item Acted as project manager, implementing tickets, pull requests, and
            continuous integration testing using GitHub.
\end{itemize}

\subsection{University of Washington, Seattle {$\parallel$}{ Bachelor of Arts in Anthropology} \hfill
      \textbf{2011}}
\begin{itemize}
      \item Top-ranking graduate, Summa cum laude
      \item Focused on Archaeology, Anthropology, Oceanography, Geology
\end{itemize}

\end{document}