\documentclass[a4paper,9pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\Large \textbf{H.R. Johnson}} \\
      {\small Full-Stack Engineer and Developer Relations Specialist in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\
      \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}}
\end{center}

\section{Summary}
{\small Experienced developer with 20+ years in technical and gaming community management. Proficient in AI/ML technologies and technical content creation. Skilled in producing blogs, guides, whitepapers, videos, and webinars. Proven ability to translate complex concepts for diverse audiences and collaborate cross-functionally. Seeking to leverage my expertise to enhance developer engagement at Scale AI.}

\section{Skills}
\textbf{Languages {$\parallel$} \normalfont{JavaScript,
            TypeScript, SQL, LaTeX}}

\textbf{Tools \& Technologies {$\parallel$} \normalfont{HTML, CSS, React, Redux, REST, Git, Express.js, Node.js, PostgreSQL, Prisma, Jest, JWT, bcrypt, Jira, HubSpot, FirstData, Apps Scripts, GitHub, VS Code, WSL, Kanban, Agile}}

\textbf{Content Creation {$\parallel$} \normalfont{Technical writing, blog posts, whitepapers, webinars}}

\section{Experience}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Produced engaging technical content including blogs, guides, and whitepapers.
      \item Designed and developed Apps Scripts for engagement and retention
            projects.
      \item Planned VIP, CEO, and Influencer publishing opportunities and community
            events and webinars.
      \item Increased user engagement from 2\% to 7\% with
            strategic
            development.
      \item Employed ChatGPT to assist in drafting and refining content, automating responses, and enhancing customer support.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Managed cross-functional teams in community forums and customer
            support.
      \item Assisted with project management, product development and UX design.
      \item Improved retention 5\% by implementing user-generated content contests.
      \item Increased moderator productivity and satisfaction ratings from 61\%
            to
            96\%.
      \item Handled customer support issues and abuse reports.
\end{itemize}

\subsection{Fullstack Academy, Remote {$\parallel$}{ Student} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development
            bootcamp.
      \item Developed advanced engineering projects, including e-commerce and gaming applications.
      \item Led projects and implemented continuous integration testing and code reviews.
\end{itemize}

\section{Education}
\textbf{University of Washington, Seattle, WA} \hfill
\textbf{2011}
\\
Bachelor of Arts in Anthropology \& Archaeology, Summa cum laude

\section{FullStack Academy Capstone Projects}

\subsection{Alley Cat: Retro Side-Scroller Game {$\parallel$}{
                  Project Manager
                  \& Developer}
      \hfill \textbf{June 2024}}
{Led a team of 4 developers in building a retro-feeling
      side-scroller game using vanilla JavaScript and HTML5 canvas.
      Implemented
      project management best practices, including tickets, lanes, and
      pull-request
      workflows. Configured GitHub for continuous integration testing and
      performed
      code reviews for the team. Code deployed at \href{https://github.com/Cherry-Stone-Studios/Cherry-Stone-Studios}{github.com/Cherry-Stone-Studios/Cherry-Stone-Studios}.}

\subsection{E-Commerce App: PokeDealers {$\parallel$}{ Developer}
      \hfill \textbf{May 2024}}
{Worked with 2 other developers on a full-stack e-commerce
      application
      to provide a user-friendly
      online shopping experience. Utilized React for the
      front-end, Express.js for
      the back-end API, and Prisma for database management. Code located
      at \href{https://github.com/Charmelions/charmelions}{github.com/Charmelions/charmelions}.}


\end{document}