\documentclass[a4paper,9pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\Large \textbf{H.R. Johnson}} \\
      {\small Full-Stack Engineer and Developer Relations Specialist in Kalamazoo, Michigan \\
      \href{tel:360-951-0354}{360-951-0354}\\
      \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}\\

      \mbox{\href{https://github.com/Find-Serendipity}{github.com/Find-Serendipity}
            \&

            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}}
\end{center}

\section{Summary}
{\small Experienced community manager with 20+ years in gaming and technical community building. Accomplished engagement professional with growing coding fundamentals, a robust understanding of blockchain and web3 technology, and a high EQ. Proven track record of business development and relationship building. Seeking to leverage my expertise to enhance developer engagement at Eclipse.}
\section{Skills}
\textbf{\small Languages {$\parallel$} \normalfont{JavaScript,
            TypeScript, SQL, LaTeX}}

\textbf{\small Tools \& Technologies {$\parallel$} \normalfont{HTML, CSS, React, Redux, Node.js, Express.js, PostgreSQL, Prisma, REST APIs, Git, Jest, JWT, bcrypt, Agile, Kanban, Jira, GitHub}}

\textbf{\small Blockchain \& Crypto: {$\parallel$} \normalfont{Blockchain Fundamentals, NFT Creation and Distribution, Crypto Trends}}

\section{Experience}
\subsection{Fullstack Academy, Remote {$\parallel$}{ Student} \hfill
      \textbf{Feb
            2024 – June
            2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web
            development
            bootcamp.
      \item Led projects implementing Agile methodologies, GitHub workflows, and continuous integration.
      \item Conducted code reviews and pair programming to maintain high code quality.
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Educated Cointelegraph clients on blockchain and crypto-related topics, and answered questions in the forums.
      \item Planned publishing opportunities and helped manage
      events and webinars for VIP communities.
      \item Increased user engagement from 2\% to 7\% with strategic development.
      \item Trained team members in community tactics and reporting.
      \item Developed engaging content strategy around blogs, guides, and whitepapers.
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Managed cross-functional teams in community forums and customer
      support.
      \item Assisted with project management, product development and UX design.
      \item Improved user retention 5\% by implementing user-generated content contests.
      \item Increased moderator productivity and satisfaction from 61\%
            to
            96\%.
      \item Handled customer support issues and abuse reports.
\end{itemize}

\section{FullStack Academy Capstone Projects}

\subsection{Alley Cat: Retro Side-Scroller Game {$\parallel$}{
                  Project Manager
                  \& Developer}
      \hfill \textbf{June 2024}}
{ Led a team of 4 developers in building a retro-feeling
      side-scroller game using vanilla JavaScript and HTML5 canvas.
      Implemented
      project management best practices. Configured continuous integration testing and
      performed
      code reviews. Code deployed at \href{https://github.com/Cherry-Stone-Studios/Alley-Cat-Game}{github.com/Cherry-Stone-Studios/Alley-Cat-Game}.}

\subsection{E-Commerce App: PokeDealers {$\parallel$}{ Developer}
      \hfill \textbf{May 2024}}
{ Worked with 2 other developers on a full-stack e-commerce
      app to provide a user-friendly shopping experience. Utilized React, Express.js and Prisma for database management. Code located
      at \href{https://github.com/Charmelions/PokeDealer}{github.com/Charmelions/PokeDealer}.}

\section{Education}
\textbf{University of Washington, Seattle, WA} \hfill
\textbf{2011}\\
Bachelor of Arts in Anthropology \& Archaeology, Summa cum laude

\end{document}