\documentclass[10pt,letterpaper]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlist[itemize]{topsep=2pt, partopsep=0pt, parsep=0pt, itemsep=3pt, leftmargin=15pt}

\input{glyphtounicode}
\pdfgentounicode=1

\hypersetup{hidelinks}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{3pt}
    Kalamazoo, MI 49007 | 360-951-0354 | \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} | \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\vspace{2.5mm}
I'm a solutions oriented and analytical professional with years of experience working in the software industry. I am an expert in fostering healthy communities, translating qualitative feedback into organized technical requirements, and building workflows that drive efficiency. I am a clear communicator committed to creating consistent, user-centered support ecosystems that respect both the developer's time and the customer's experience.
\vspace{1mm}

\section{Technical Skills \& Core Competencies}
\begin{itemize}
    \item \textbf{Support Operations, Compliance \& Administration:} Support pod leadership (10+ agents), ticketing queue routing, response time reduction, backlog triage, macro design, help center content strategy, custom reporting dashboards, SLA compliance, QA scorecards, onboarding playbook design, SOP creation, KPI tracking, high-sensitivity record management, report preparation, and data entry.
    \item \textbf{Technical Engineering \& SDLC Fluency:} Full-stack web development (HTML5, CSS3, JavaScript, TypeScript, React.js, Next.js, Redux, Node.js, Express.js), database architecture (PostgreSQL, SQL, JSON, Prisma), Git version control (branching strategies), CI/CD concepts, development pipelines, automated testing (Jest), and authentication (JWT, bcrypt).
    \item \textbf{Workflow Automation, APIs \& AI Literacy:} Generative AI workflows, prompt engineering, custom script-based reporting automation (Google Apps Script), programmatic typesetting (LaTeX), data collation pipelines, system integration logic, REST API logic, and data analysis.
    \item \textbf{Technical Support, Community Strategy \& Regulated Systems:} Troubleshooting PC hardware/software, knowledge base creation, bug reporting, managing data within highly regulated environments (Epic Software), global community management, user engagement \& retention, content strategy, forum moderation, incident escalation, and empathetic user communication.
    \item \textbf{Product Strategy, Client Success \& Methodologies:} Strategic account health tracking, churn mitigation, technical scoping, data-driven prioritization, experiment analysis, A/B testing insights, discovery workshops, UX/UI feedback loops, SEO principles, cross-functional engineering partnerships, Agile, Scrum, and Kanban.
\item \textbf{Platforms \& Ecosystems:} Jira, Confluence, Zendesk, HubSpot CRM, Blackbaud Altru, Hootsuite, Canva, WordPress, MailChimp, Adobe Creative Suite (Photoshop, InDesign, Illustrator), Google Workspace (Docs, Sheets, Slides), Microsoft Office Suite (Advanced Word, Excel, PowerPoint), FirstData, GitHub, GitHub Actions, Docker, Linux, WSL, and VS Code.
\end{itemize}

\section{Professional Experience}

\textbf{Customer Experience Technician} | Family Health Center (Kalamazoo, MI) \hfill March 2026 - Present
\begin{itemize}
    \item Manage patient intake, registration pipelines, and front-desk switchboard routing inside a Federally Qualified Health Center (FQHC).
    \item Optimized scheduling workflows by utilizing the Epic Daily Appointments Report, reducing provider schedule auditing time from one hour to five minutes.
    \item Verify and input patient demographic, insurance, and billing data to prevent downstream processing friction and billing errors.
    \item Troubleshoot scheduling requirements and coordinate front-desk patient flow while maintaining data confidentiality under HIPAA regulations.
    \item Execute point-of-service fee collections, tally shift balances, and manage closing balance sheets according to clinic cash policies.
\end{itemize}

\textbf{Founder} | Communitrix (Remote) \hfill September 2023 - Present
\begin{itemize}
    \item Developed and managed targeted community launch plans and platform configurations based on individual client needs.
    \item Built custom generative AI prompt workflows to rapidly draft project scopes, service contracts, and policy guidelines.
    \item Analyzed forum and social platform engagement metrics to deliver clear, data-driven growth updates to business stakeholders.
    \item Rebuilt client website using modern web frameworks to upgrade security, improve site maintainability, and modernize layouts, including for mobile devices.
\end{itemize}

\textbf{Guest Experience Ambassador} | AirZoo Aviation Museum (Portage, MI) \hfill August 2024 - Present
\begin{itemize}
    \item Operated the ticket desk, serving as the first point of contact for visitors, and manage front-desk communications including phone calls and mail distribution.
    \item Managed guest check-ins, new member registrations, and institutional reporting with Altru. 
    \item Assisted with membership services, including data entry, creating reports with graphs and charts, and assembling welcome materials.
    \item Applied conflict resolution and active listening to address guest concerns and foster a welcoming environment.
    \item Analyzed membership data to prepare reports for senior leadership, highlighting impact of attendance from specific communities with Altru.
\end{itemize}

\textbf{Community Manager} | Community.co (Remote) \hfill July 2019 - May 2023
\begin{itemize}
    \item Programmed custom Google Apps Scripts to automate metric collection pipelines, user engagement tracking, and retention analytics.
    \item Coordinated high-sensitivity executive publishing workflows and interactive event schedules for Forbes Councils, Newsweek Expert Forum, and Fast Company Executive Board.
    \item Created, monitored, and analyzed KPIs to achieve targeted platform growth and engagement milestones.
    \item Increased active platform user engagement from 2\% to 7\% through data-driven interaction strategies and systematic interface moderation.
    \item Trained incoming team members on internal platform tools, database reporting systems, and technical workflow documentation.
\end{itemize}

\textbf{Community Manager} | Internet Brands (Los Angeles, CA) \hfill September 2013 - July 2019
\begin{itemize}
    \item Managed multi-tier, cross-functional moderation teams and platform operational support queues across a high-volume multi-vertical website portfolio.
    \item Increased portfolio customer satisfaction ratings from 61\% to 96\% over a 24-month period by isolating operational friction and optimizing queue response times.
    \item Designed and executed user-generated content campaigns and community retention events to stabilize long-term platform traffic.
    \item Resolved advanced user support escalations, technical system friction, platform integrity bugs, and systemic abuse reports.
    \item Authored technical site documentation, feature updates, user guides, and comprehensive system whitepapers.
\end{itemize}

\textbf{Community Manager} | Breaktime Studio (San Francisco, CA) \hfill January 2013 - August 2013
\begin{itemize}
    \item Managed active social platform channels and customer support ticketing queues for 8 concurrent mobile gaming titles.
    \item Increased core brand page following by 50\% using targeted audience delivery loops and structured communication schedules.
    \item Isolated, filtered, and translated real-time community bug feedback into technical inputs to build a prioritized product release schedule for the engineering team.
\end{itemize}

\textbf{Community Liaison} | Zynga (Remote) \hfill May 2009 - December 2012
\begin{itemize}
    \item Monitored and moderated high-volume iOS mobile gaming forums to protect platform health and enforce user policies.
    \item Documented real-time community sentiment shifts and isolated system-level anomalies, reporting directly to core engineering teams to guide patch loops.
    \item Produced technical player documentation, gameplay tutorials, feature release logs, and instructional video guides.
\end{itemize}

\section{Education}

\textbf{Full-Stack Academy} | Full-Stack Web Dev Technical Certificate (Remote) \hfill Graduate, Top of Class - 2024
\begin{itemize}
    \item Built and deployed interactive full-stack web applications within collaborative, agile development settings, acquiring deep fluency in modern web ecosystems.
    \item Managed team codebases and deployment lifecycles using Git version control, explicitly handling feature branching, repository architecture, and resolving complex merge conflicts.
\end{itemize}

\textbf{University of Washington} | B.A. Anthropology, \textit{focus in Archaeology} (Seattle) \hfill Magna Cum Laude - 2011
\begin{itemize}
    \item Spent dedicated time in the Burke Museum cataloging and rehousing artifacts for public display.
    \item Conducted extensive laboratory work cleaning, analyzing, and cataloging archaeological artifacts.
\end{itemize}

\end{document}