\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.1em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Kalamazoo, MI {$\parallel$} (360) 951-0354 {$\parallel$} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} {$\parallel$} \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\paragraph{Dynamic, logically-driven Technical Success Manager with 7+ years of experience bridging the gap between non-technical stakeholders and complex software environments. Combines robust full-stack engineering logic with a deep background in customer adoption, documentation writing, and technical support triage. Skilled at scaling enablement programs, optimizing customer onboarding paths, and interpreting software feedback to drive retention.}

\subsubsection{\underline{Core Competencies}}

\begin{itemize}
    \item \textbf{Technical Customer Success \& Support:} Developer relations, stakeholder management, user onboarding workflows, churn risk reduction, data telemetry interpretation, technical escalation pathing.
    \item \textbf{Enablement \& Technical Documentation:} Authoring complex knowledge base guides, procedural checklists, FAQs, user tutorials, and functional UX wireframes for engineering sprints.
    \item \textbf{Software Logic \& Infrastructure:} JavaScript, SQL, GitHub Actions, custom Google Apps Script automation, bug tracking tools, Agile/Kanban software development lifecycles.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Technical Success \& Operations Consultant} {$\parallel$} \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Consult for digital product communities to optimize user software adoption, authoring central developer documentation, comprehensive FAQs, and structured technical guides.
      \item Diagnose and troubleshoot technical user environment configurations, peripheral software integrations, and custom logic issues.
      \item Leverage generative AI and automated scripts to accelerate administrative output, scale metrics pipelines, and build client-facing reporting assets.
\end{itemize}
\vspace{1.5mm}
{\textbf{Technical Customer Success Manager} {$\parallel$} \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Managed campaign lifecycles and retention health for high-profile client networks, driving platform-wide engagement metrics up from 2\% to 7\%.
      \item Programmed custom Google Apps Scripts to automate administrative workflows, streamline complex system reporting, and ingest clean user telemetry.
      \item Mediated technical product requirements and active software bug logs, serving as the core translation link between external business partners and internal engineering squads.
      \item Recruited, trained, and managed a distributed team of operations contractors focused on high-quality data collection and technical support accuracy.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Success Specialist \& UX Liaison} {$\parallel$} \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Administered high-volume user systems, boosting overall customer satisfaction from 61\% to 96\% through targeted product enablement and proactive account health tracking.
      \item Authored internal and public-facing technical support documentation, product feature tutorials, and initial wireframes to inform active developer sprints.
      \item Directed multi-tiered user moderation programs, overseeing rapid daily support ticket triage and critical event escalation paths.
\end{itemize}
\vspace{1.5mm}
{\textbf{Technical Support Triage Coordinator} {$\parallel$} \textit{Breaktime Studios,}  \textbf{Remote} \hfill {Jan 2013 – July 2013}}
\begin{itemize}
      \item Managed live-ops support pipelines for mobile software applications, acting as the primary feedback link between a global player base and core engineering teams.
      \item Aggregated, structured, and prioritized technical user feedback, user application crash logs, and telemetry data to guide upcoming sprint planning cycles.
\end{itemize}

\subsubsection{\underline{Technical Projects \& Cross-Functional Leadership}}

{\textbf{Project Manager \& Developer} \textit{$\parallel$ Fullstack Academy Capstone Project} \hfill {June 2024}}
\begin{itemize}
      \item Led a 4-person technical team through software delivery pipelines, governing project milestones, code reviews, and cross-functional task delegation using GitHub.
      \item Conducted extensive user feedback collection rounds to isolate customer experience points of friction, refining product logic to increase system usability.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} {$\parallel$} Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} {$\parallel$} Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}