\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

\titleformat{\section}{\large\bfseries}{\thesection}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5ex}{1ex}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{1mm}
    Kalamazoo, MI 49007 \textbar{} \href{tel:360-951-0354}{360-951-0354} \textbar{} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}
\end{center}

\section{Objective}
A detail-oriented and organized professional with over two years of experience in customer service and administrative support. Seeking to leverage strong communication skills and proficiency in office procedures to contribute effectively as a Receptionist or Administrative Assistant. Eager to provide exceptional service and support in a dynamic office environment.

\section{Skills}

\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Office Administration:} Microsoft Office Suite (Word, Excel), Google Suite, Data Entry, Report Preparation, Filing, Scheduling, Mail Processing, Answering \& Screening Calls.
    \item \textbf{Customer Service:} Exceptional Written and Verbal Communication, Guest Reception, Needs Assessment, Problem Resolution, Confidentiality, and Client Support.
    \item \textbf{Professional Attributes:} Highly Organized, Strong Prioritization \& Time Management, Detail-Oriented, Adaptable, Dependable, Team-Oriented, and Trustworthy.
\end{itemize}

\section{Experience}

\textbf{Guest Experience Ambassador} \hfill \textbf{Aug 2024 -- Current} \\
\textit{Air Zoo Aviation Museum, Portage, MI}
\begin{itemize}[leftmargin=*, nosep]
    \item Operated the ticket desk, serving as the first point of contact for visitors, and manage front-desk communications including phone calls and mail distribution.
    \item Assisted with membership services, including data entry, creating reports with graphs and charts, and assembling welcome materials.
    \item Applied conflict resolution and active listening skills to address guest concerns and foster a welcoming environment.
    \item Gathered and analyzed membership data to prepare reports for investors, highlighting community impact in specific neighborhoods.
    \item Provided safe and timely transportation for guests between campus locations via the shuttle service.
\end{itemize}
\vspace{0.5em}
\textbf{Freelance Project Support} \hfill \textbf{Sep 2023 -- Current} \\
\textit{Communitrix, Remote}
\begin{itemize}[leftmargin=*, nosep]
    \item Provided dedicated administrative and customer support to a diverse client base, ensuring clear and effective communication.
    \item Managed and maintain confidential client records, ensuring all project data is accurate and up-to-date.
    \item Organized and prioritize numerous tasks to meet deadlines and support client objectives.
\end{itemize}
\vspace{0.5em}
\textbf{Community Support} \hfill \textbf{July 2019 -- June 2023} \\
\textit{Community.co, Remote}
\begin{itemize}[leftmargin=*, nosep]
    \item Compiled and analyzed community data to prepare weekly reports with visual aids for stakeholders.
    \item Delivered timely and helpful customer support to members via email and online forums, accurately assessing their needs.
    \item Maintained organized records regarding memberships, events, and member activities, ensuring data integrity.
\end{itemize}

\section{Education}

\textbf{Fullstack Academy} \hfill \textbf{Top of Class} \\
\textit{Completed intensive program in Fullstack development.}

\textbf{University of Washington} \hfill \textbf{Magna Cum Laude} \\
\textit{Bachelor of Arts}

\textbf{Shelton High School} \hfill \textbf{Summa Cum Laude} \\
\textit{Diploma}
\end{document}
