\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

\titleformat{\section}{\large\bfseries}{\thesection}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5ex}{1ex}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{1mm}
    Kalamazoo, MI 49007 \textbar{} \href{tel:360-951-0354}{360-951-0354} \textbar{} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}
\end{center}

\section{Objective}
A creative and detail-oriented professional with over a decade of home baking experience seeking a full-time position. Eager to apply a passion for baking to a professional bakery environment.
\section{Skills}

\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Baking \& Culinary Skills:} Cakes, Cupcakes, Cookies, Pies, Recipe Development, Food Safety, Kitchen Hygiene.
    \item \textbf{Customer Service \& Communication:} Written \& Verbal Communication, Problem Resolution, Client Support, Customer Engagement.
    \item \textbf{Professional Attributes:} Highly Organized, Strong Prioritization, Detail-Oriented, Adaptable, Team-Oriented, Trustworthy.
\end{itemize}

\section{Experience}

\textbf{Assistant Baker} \hfill \textbf{Sep 2025 -- Current} \\
\textit{Kzoo Cream Cookies, Kalamazoo, MI}
\begin{itemize}[leftmargin=*, nosep]
    \item Baked a variety of cookies to meet customer demand, ensuring high quality and consistency.
    \item Collaborated with owner to ensure safe and efficient kitchen operations.
    \item Assisted in developing new recipes, contributing to menu innovation and customer satisfaction.
    \item Maintained a clean and organized kitchen environment, adhering to food safety standards.
    \item Participated in Pumpkin Soiree 2025, contributing cake and customer engagement at the booth.
\end{itemize}
\vspace{0.5em}
\textbf{Guest Experience Ambassador} \hfill \textbf{Aug 2024 -- Current} \\
\textit{Air Zoo Aviation Museum, Portage, MI}
\begin{itemize}[leftmargin=*, nosep]
    \item Operated the ticket desk taking payments, answering phones, and managing customer service.
    \item Assisted with member services, including data entry, reports, and assembling member materials.
    \item Managed ride operations, ensuring guest safety and satisfaction.
    \item Provided safe and timely transportation for guests between campus locations via the shuttle service.
\end{itemize}
\vspace{0.5em}
\textbf{Freelance Project Support} \hfill \textbf{Sep 2023 -- Current} \\
\textit{Communitrix, Kalamazoo, MI}
\begin{itemize}[leftmargin=*, nosep]
    \item Provided administrative and customer support to a diverse client base, ensuring clear communication.
    \item Managed and maintained client records, ensuring all data is confidential, accurate and up-to-date.
    \item Organized and prioritize numerous tasks to meet deadlines and support client objectives.
\end{itemize}
\vspace{0.5em}
\textbf{Community Manager} \hfill \textbf{Sep 2023 -- Current} \\
\textit{Community.co, Remote}
\begin{itemize}[leftmargin=*, nosep]
    \item Managed online communities for clients, providing timely support and troubleshooting.
    \item Moderated community spaces, fostering a welcoming and helpful atmosphere.
    \item Coordinated with technical teams to report bugs and communicate user feedback.
    \item Produced support content and documentation for common issues.
\end{itemize}

\section{Education}

\textbf{Fullstack Academy} \hfill \textbf{Top of Class} \\
\textit{Completed intensive program in Fullstack development.}

\textbf{University of Washington} \hfill \textbf{Magna Cum Laude} \\
\textit{Bachelor of Arts}
\end{document}
