\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.1em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Kalamazoo, MI {$\parallel$} (360) 951-0354 {$\parallel$} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} {$\parallel$} \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\paragraph{Strategic Developer Community Manager with 7+ years of experience bridging the gap between engineering and marketing. Uses full-stack training, AI-driven automation, and data telemetry to scale digital campaigns, nurture open-source ecosystems, and deliver high-impact insights to executive partners.}

\subsubsection{\underline{Core Competencies}}

\begin{itemize}
    \item \textbf{Developer Relations \& Data Analysis:} Developer workflows, GitHub environments, open-source etiquette, technical content, developer ecosystems, tracking KPIs, translating community data into visual wrap-ups, custom Google Apps Script automation.
    \item \textbf{Community \& Project Management:} Platform administration, scale moderation programs, user support triage, Discord/forum management, incident escalation, end-to-end campaign lifecycles, Agile/Kanban, cross-functional collaboration.
    \item \textbf{Technical Engineering \& Architecture:} JavaScript, TypeScript, React, Node.js, SQL, Git, GitHub Actions, automated testing.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Founder \& Tech Community Consultant} {$\parallel$} \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Consult for technical communities, engineering static web assets and building central developer documentation, Knowledge Bases, and comprehensive FAQs.
      \item Resolve complex developer-adjacent hardware configurations, custom rig builds, firmware updates, and peripheral software integrations.
      \item Leverage generative AI workflows to accelerate administrative tasks, generate data tracking queries, and automate delivery pipelines.
\end{itemize}
\vspace{1.5mm}
{\textbf{Community Manager} {$\parallel$} \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Managed campaign lifecycles for high-profile client networks, successfully scaling platform engagement metrics from 2\% up to 7\%.
      \item Programmed custom Google Apps Scripts to automate community workflows, streamline reporting, and capture clean user feedback loops.
      \item Recruited, trained, and managed a distributed team of contractors and support associates in data collection and performance reporting.
      \item Mediated technical feature requests and software bug trackers cross-functional between external partners and internal engineering teams.
\end{itemize}
\vspace{1.5mm}
{\textbf{Community Manager \& UX Liaison} {$\parallel$} \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Administered high-volume platforms, increasing customer satisfaction from 61\% to 96\% via targeted community initiatives.
      \item Authored technical support documentation, user tutorials, and functional UX wireframes for active engineering sprints.
      \item Directed large-scale forum moderation programs, overseeing daily support ticket triage and resolution workflows.
\end{itemize}
\vspace{1.5mm}
{\textbf{Community Manager} {$\parallel$} \textit{Breaktime Studios,}  \textbf{Remote} \hfill {Jan 2013 – July 2013}}
\begin{itemize}
      \item Coordinated mobile gaming live-ops, acting as the primary link between global player bases and engineering teams.
      \item Aggregated and prioritized technical user feedback, crash logs, and bug telemetry to guide active sprint cycles.
\end{itemize}

\subsubsection{\underline{Technical Projects \& Software Engineering Exposure}}

{\textbf{Project Manager \& Developer} \textit{Fullstack Academy Capstone Cherry Stone Studios} \hfill {June 2024}}
\begin{itemize}
      \item Led a 4-developer engineering pod, governing the deployment pipeline using GitHub, pull request reviews, and continuous integration (CI) testing.
      \item Ran public usability play-testing blocks to capture community feedback and systematically optimize core user experience constraints.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} {$\parallel$} Top-Ranking Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} {$\parallel$} Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}