% filepath: /home/icklekins/documents/resumeCM.tex
\documentclass[a4paper,12pt]{article} % Changed font size to 12pt
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} % Kept 1-inch margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\Large\bfseries}{\thesection}{0.5em}{}[\titlerule] % Increased section header size
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}
\titlespacing*{\section}{0pt}{2.0ex plus .1ex minus .2ex}{0.1in plus 1pt minus 1pt} % Adjusted space AFTER section titles/rules to 0.1in
\titlespacing*{\subsection}{0pt}{0.2in plus 2pt minus 1pt}{0.8ex plus .1ex} % Increased space BEFORE subsection titles to at least 0.2in

% Adjust paragraph spacing
\setlength{\parskip}{0.75em} % Kept at 75% of current font size (now 12pt)
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize and set indentation
\setlist[itemize]{nosep, leftmargin=0.5in} % Indent itemize lists by 0.50 inches

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{1mm}
    Kalamazoo, MI \textbar{} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \textbar{} \href{tel:360-951-0354}{360-951-0354} \textbar{} \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

% --- SUMMARY ---
\section{Summary}
Experienced Community Manager and Technical Support Specialist with a strong background in gaming communities and PC hardware. Skilled in providing friendly, effective support and troubleshooting for users of all technical levels. Adept at moderating Discord and forum spaces, documenting solutions, and collaborating with development teams. Passionate about creating positive user experiences and helping others enjoy their setups.

% --- SKILLS ---
\section{Core Competencies}
\begin{itemize}
    \item \textbf{Technical Support:} Troubleshooting PC hardware and software issues, RGB device compatibility, Knowledge Base documentation, User feedback collection
    \item \textbf{Community Management:} Discord and forum moderation, Support content creation (guides, FAQs), Positive and empathetic user communication
    \item \textbf{Gaming \& Hardware:} Familiarity with RGB ecosystems (Corsair, Razer, Logitech, etc.), PC building, Gaming culture
    \item \textbf{Web Development:} Static Website Development (HTML, CSS, JavaScript), Website Maintenance \& Security, Bug Troubleshooting
    \item \textbf{Tools \& Platforms:} Discord, Google Suite, Adobe Creative Suite, WordPress, Jira, Git, CMS \& Forum Platforms
\end{itemize}

% --- EXPERIENCE ---
\section{Professional Experience}

\subsection{Founder, Community \& Web Development Consultant \hfill Sep 2023 – Present}
\textit{Communitrix, Remote}
\begin{itemize}
    \item Provide technical support and troubleshooting for client communities, including PC hardware and software issues.
    \item Moderate Discord and forum channels, maintaining a positive and helpful environment.
    \item Develop, maintain, and optimize static websites for a diverse client base, utilizing HTML, CSS, and JavaScript.
    \item Create support content such as guides and FAQs to assist users.
\end{itemize}

\subsection{Community Manager \hfill July 2019 – June 2023}
\textit{Community.co, Remote}
\begin{itemize}
    \item Managed and supported online communities for major publications, providing timely assistance and troubleshooting for members.
    \item Moderated Discord and forum spaces, fostering a welcoming and helpful atmosphere.
    \item Coordinated with technical teams to report bugs and communicate user feedback.
    \item Produced support content and documentation for common issues.
\end{itemize}

\subsection{Community \& Customer Service Manager \hfill July 2013 – July 2019}
\textit{Internet Brands / Model Mayhem, El Segundo, CA}
\begin{itemize}
    \item Provided technical and customer support for a large online community, resolving user issues and documenting solutions.
    \item Moderated community spaces and maintained a positive environment.
    \item Created support guides and tutorials for users of varying expertise levels.
\end{itemize}

\subsection{Community Manager, Gaming \hfill Jan 2013 – July 2013}
\textit{Breaktime Studios, Remote}
\begin{itemize}
    \item Managed gaming communities and acted as the primary liaison between players and developers.
    \item Gathered and organized user feedback to help prioritize feature requests and improvements.
    \item Stayed current with new hardware and software releases relevant to gaming communities.
\end{itemize}

\subsection{Social Media Strategist \& Community Moderator \hfill 2009 – 2013}
\textit{Metaverse Mod Squad \& Zynga Games, Remote}
\begin{itemize}
    \item Provided community moderation and technical support for gaming clients, including Discord and forums.
    \item Authored guides, FAQs, and weekly reports on community trends and common issues.
    \item Supported player retention through clear communication and helpful resources.
\end{itemize}

% --- EDUCATION & TECHNICAL TRAINING ---
\section{Education \& Technical Training}
\subsection{Fullstack Academy, Remote \hfill 2024}
\textit{Top-Ranking Graduate, Full-Stack Web Development Bootcamp}
\begin{itemize}
    \item Completed an immersive program focused on modern web technologies, including JavaScript, React, and Node.js.
    \item Acted as project manager for capstone projects, implementing tickets, pull requests, and CI testing using GitHub.
\end{itemize}

\subsection{University of Washington, Seattle \hfill}
\textit{Bachelor of Arts in Anthropology, Summa cum laude}

\end{document}