\documentclass[a4paper,10pt]{article}
\usepackage[left=0.70in, right=0.70in, top=0.70in, bottom=0.70in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.4em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em} % Adjusted for more space between paragraphs
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}
\begin{center} % Center-justify content
      {\LARGE \textbf{H.R. Johnson}} \\
      Community-Driven in Kalamazoo, Michigan \\
      \mbox{\href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \&
            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}\\
      \href{tel:360-951-0354}{360-951-0354}

\end{center}

\section{Summary }
\noindent
Experienced professional with 15+ years in customer service and community management. Excellent communication and interpersonal skills, with a commitment to excellence and attention to detail. Adherent to high standards while working to understand, meet, and exceed client expectations.

\section{Skills}
\textbf{Languages {$\parallel$}} \small{{ French (Intermediate),
            JavaScript, TypeScript, SQL, LaTeX, PHP}}

\textbf{Tools and Technologies {$\parallel$}} \small{{ HTML, CSS, React.js, REST, Git, Express.js, Node.js, Next.js, Jira, HubSpot CRM, Apps Scripts, Miro, Figma, Canva, Hootsuite, Zendesk, Microsoft Suite, 
            GitHub, VS Code, WSL, Docker, Linux, Kanban, Agile, A/B Testing, Facebook, Instagram, X/Twitter, Discord, Telegram, Reddit, LinkedIn}}

\textbf{Proficiencies {$\parallel$}} \small{{Customer Service, Sales, Community Management, Social Media Management, Customer Support, Event Management, Crisis Management}}

\section{Experience}

\subsection{Air Zoo Aviation Museum, Kalamazoo, MI {$\parallel$}{
                  Guest Experience Ambassador} \hfill
      \textbf{Aug 24 – Current}}
\begin{itemize}
      \item Handled cash, inventory, and front desk duties including adding customers to member database.
      \item Guided guests through museum experience while operating from a stationary assignment.
      \item Engaged guests in a fast-paced environment, providing detailed answers about planes, artifacts, and the museum.
      \item Helped manage flow of crowds, efficiently helping guests with needs and
            directing as needed.
      \item Ensured guest safety in various situations with various crowd sizes.
\end{itemize}

\subsection{Communitrix, Remote {$\parallel$}{ Founder} \hfill
      \textbf{Sep 2023 – Current}}
\begin{itemize}
      \item Obtained and maintained a small but strong client base.
      \item Drafted and implemented community management plans for clients, including social strategies for Facebook and Reddit.
      \item Maintained specific client codebases, updating sites to maintain modern security protocols.
      \item Created standard and milestone-based contracts for all work started with clients.
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June
            2023}}
\begin{itemize}
      \item Upsold events and memberships to members via forums and email marketing campaigns
      \item Managed communities for various high-profile clients, increasing
            community engagement from 2\% to 7\%
      \item Designed and developed Google Apps Scripts for engagement and retention
            projects
      \item Trained team members in data collection, analysis, and reporting
\end{itemize}

\subsection{Internet Brands, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July
            2019}}
\begin{itemize}
      \item Created incentives for members to purchase larger or longer memberships
      \item Managed cross-functional teams in community forums and customer support
      \item Increased customer satisfaction from 61\% to 96\% through strategic
            initiatives
      \item Handled customer support issues and abuse reports
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$} {Junior Developer} \hfill
      \textbf{Feb
            2024 – June
            2024}}

\subsection{University of Washington, Seattle {$\parallel$}{ Bachelor of Arts
                  in Anthropology} \hfill
      \textbf{2011}}
\begin{itemize}
      \item Top-ranking graduate, Summa cum laude
\end{itemize}

\end{document}