\documentclass[a4paper,11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em} % Reduced from 1em

\titleformat{\section}{\large\bfseries}{\thesection}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5ex}{1ex}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{1mm}
    Kalamazoo, MI 49007 \textbar{} \href{tel:360-951-0354}{360-951-0354} \textbar{} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com}
\end{center}

\section{Objective}
A reliable and detail-oriented professional with a strong dedication to safety, seeking to apply data management skills to the Administrative Officer position at Securitas. Eager to contribute to a secure environment through attention to detail and accurate data handling.

\section{Skills}

\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Office Skills:} Microsoft Office Suite (Excel, Word, PowerPoint), Google Suite (Sheets, Docs, Slides), Data Entry \& Analysis, Report Preparation, Customer Service.
    \item \textbf{Customer Service:} Excellent Written and Verbal Communication, Guest Support and Assistance, Problem Resolution, Community Engagement.
    \item \textbf{Professional Skills:} Prioritization, Time Management, Independent Worker, Adaptable, Strong Work Ethic, Reliable, Trustworthy.
\end{itemize}

\section{Experience}

\textbf{Guest Experience Ambassador} \hfill \textbf{Aug 2024 -- Current} \\
\textit{Air Zoo Aviation Museum, Portage, MI}
\begin{itemize}[leftmargin=*, nosep]
    \item Deliver excellent customer service by proactively assisting guests, resolving inquiries, and maintaining a welcoming and safe environment.
    \item Use Microsoft Excel to compile and analyze membership data, creating graphs, tables, and charts for membership reports.
    \item Work independently to manage daily tasks and responsibilities with a high degree of attention to detail.
\end{itemize}
\vspace{0.5em}
\textbf{Freelance Project Support} \hfill \textbf{Sep 2023 -- Current} \\
\textit{Communitrix, Remote}
\begin{itemize}[leftmargin=*, nosep]
    \item Provide dedicated administrative and customer support to a diverse client base, ensuring clear communication.
    \item Handle client records and ensure all project data is accurate and maintained.
\end{itemize}
\vspace{0.5em}
\textbf{Community Support} \hfill \textbf{July 2019 -- June 2023} \\
\textit{Community.co, Remote}
\begin{itemize}[leftmargin=*, nosep]
    \item Compiled and analyzed community data to prepare weekly reports with visual aids for stakeholders using Excel.
    \item Delivered timely and helpful customer support to members via email and online forums.
    \item Maintained organized records regarding memberships, events and member activities.
\end{itemize}

\section{Education}

\textbf{Fullstack Academy} \hfill \textbf{2024} \\
\textit{Completed intensive program in Fullstack development.}

\textbf{Shelton High School} \hfill \textbf{High School Diploma} \\
\textit{Located in Shelton, WA}

\end{document}