\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

\setcounter{secnumdepth}{0}

\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

\setlength{\parskip}{0.1em} 
\setlength{\parindent}{0em} 

\setlist{nosep, leftmargin=*}

\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
            Kalamazoo, MI  $\parallel$  (360) 951-0354 $\parallel$  \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} $\parallel$  \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity} 
\end{center}

\vspace{4mm}
Solutions oriented, analytical and efficient, with over 7 years of working collaboratively and clearly communicating in a remote, professional environment. Self-taught and academy trained in full stack web development. Experienced in breaking friction points down into structured technical specs, workflow optimization, and data analysis. Proven ability to translate user feedback into clear product and system requirements.
\vspace{2mm}

\subsubsection{\underline{Core Competencies}}
\begin{itemize}
    \item \textbf{Customer Success \& Advocacy:} Cross-functional collaboration, workshop facilitation, KPI creation, KPI tracking, post-sales adoption, value realization, product advocacy.
    \item \textbf{Technical \& SDLC Fluency:} Git version control, branching strategies, CI/CD concepts, development pipelines, front \& back-end architecture, API integration logic, collaborative troubleshooting.
    \item \textbf{Operational Efficiency \& AI Integration:} Generative AI workflows, prompt engineering, technical writing \& documentation, operational change management.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Community Product Consultant} $\parallel$ \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Developed and executed custom community management and social media strategies for clients to optimize user acquisition and digital engagement.
      \item Leveraged generative AI prompt workflows to rapidly draft project scopes, client service contracts, and operational requirements.
      \item Analyzed client operational and engagement data to generate structured performance reports and actionable strategic insights for stakeholders.
      \item Rebuilt client website utilizing modern frameworks to upgrade security standards, improve site stability, and enhance the overall user experience.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Success \& Support Operations Manager} $\parallel$ \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Acted as the main customer success lead for enterprise clients, championing the product and clearing out user hurdles so they could get the most value out of our platform.
      \item Worked with account managers to redesign outbound emails and guides, using user behavior data to help people engage more naturally with the product.
      \item Wrote custom Google Apps Scripts to automate manual reporting, which cut out friction and helped boost forum participation from 2\% to 7\%.
      \item Tracked customer engagement data to set realistic performance goals, successfully raising user response and conversion rates to 10\%.
      \item Worked as the main bridge between users and the engineering team, turning qualitative user complaints and feedback into clear, structured quantitative reports and build requirements for the developers.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Support Specialist \& UX Liaison} $\parallel$ \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Sorted through high-volume support queues to fix bugs and help users, improving our internal triage steps to raise customer satisfaction from 61\% to 96\%.
      \item Collaborated directly with product managers and UX teams to systematically capture usability friction points and inform platform roadmap priorities.
      \item Developed rigorous, data informed operational checklists and training guides to standardize performance across remote support teams.
    \end{itemize}

\subsubsection{\underline{Technical Projects \& Collaboration}}
{\textbf{Product \& Project Manager (Technical Pod Lead)} $\parallel$ \textit{Fullstack Academy Capstone} \hfill {June 2024}}
\begin{itemize}
      \item Led a small developer team to build a web-based retro game in two weeks, using Git version control and simple Kanban boards to keep our code organized and our delivery on time.
      \item Managed our development steps, ran daily standups, and set up quick workshops to help the team troubleshoot code and design the game's architecture.
      \item Looked at user playtest feedback and translated it into quick bug-fix tasks, prioritizing critical database and user interface fixes so the game ran smoothly.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} $\parallel$ Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} $\parallel$ Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}