\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

\setcounter{secnumdepth}{0}

\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

\setlength{\parskip}{0.1em} 
\setlength{\parindent}{0em} 

\setlist{nosep, leftmargin=*}

\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
            Kalamazoo, MI $\parallel$ (360) 951-0354 $\parallel$ \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} $\parallel$ \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity} 
\end{center}

\vspace{2mm}
Solutions oriented and analytical, with a background in full stack software development and 7+ years working collaboratively and clearly communicating in a professional environment. Expert at breaking down ambiguous user friction points into structured technical specs, optimizing workflow pipelines, and analyzing metrics to drive data informed decisions. Proven ability to translate user feedback into clear product requirements.
\vspace{1.5mm}

\subsubsection{\underline{Core Competencies}}
\begin{itemize}
    \item \textbf{Product Strategy \& Requirements:} Technical scoping, data-driven prioritization, user persona empathy, experiment analysis, A/B testing insights, cross-functional collaboration, technical writing.
    \item \textbf{Workflow Automation \& AI Literacy:} Prompt engineering, custom automation loops (Google Apps Script), system integration logic, workflow optimization, data collation pipelines.
    \item \textbf{Cross-Functional Collaboration:} Agile/Kanban frameworks, engineering partnership, stakeholder management, discovery workshops, UX/UI feedback loops, Zendesk and ticketing ecosystems.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Community Product Consultant} $\parallel$ \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Developed and executed custom community management and social media strategies for clients to optimize user acquisition and digital engagement.
      \item Leveraged generative AI prompt workflows to rapidly draft project scopes, client service contracts, and operational requirements.
      \item Analyzed client operational and engagement data to generate structured performance reports and actionable strategic insights for stakeholders.
      \item Rebuilt client website utilizing modern frameworks to upgrade security standards, improve site stability, and enhance the overall user experience.
\end{itemize}
\vspace{2mm}
{\textbf{Customer Success \& Support Operations Manager} $\parallel$ \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Acted as a core liaison between high-touch enterprise users and internal software engineering squads, translating raw user feature requests into clear development specs.
      \item Programmed custom Google Apps Scripts to automate repetitive reporting mechanisms, optimizing feedback collation pipelines and driving user community forum engagement from 2\% to 7\%.
      \item Partnered cross-functionally with Account Managers to redesign outbound customer communications, aligning company strategic messaging with user behavioral insights to optimize platform engagement.
      \item Analyzed communication interaction data and layout performance to refine messaging strategy, successfully increasing user conversion and response rates from a 7\% baseline up to 10\%.
\end{itemize}
\vspace{2mm}
{\textbf{Customer Support Specialist \& UX Liaison} $\parallel$ \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Evaluated high volume user feedback and bugs across complex platform ticketing environments, optimizing internal triage patterns to elevate customer satisfaction from 61\% to 96\%.
      \item Collaborated directly with product managers and UX teams to systematically capture usability friction points and inform platform roadmap priorities.
      \item Developed rigorous, data informed operational checklists and training guides to standardize performance across remote support teams.
\end{itemize}

\subsubsection{\underline{Technical Projects \& Product Leadership}}
{\textbf{Product \& Project Manager (Technical Pod Lead)} $\parallel$ \textit{Fullstack Academy Capstone} \hfill {June 2024}}
\begin{itemize}
      \item Orchestrated the 2-week development of \textit{Alley Cat} (a web-based retro game), using Agile/Kanban frameworks to define the MVP feature set and keep delivery strictly on schedule.
      \item Facilitated team momentum and execution through strength-based task delegation and collaborative troubleshooting.
      \item Translated cohort playtest data into actionable technical fixes, prioritizing critical bugs across the user registration database and front-end interface to deliver a polished user experience.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} $\parallel$ Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} $\parallel$ Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}