\documentclass[a4paper,12pt]{article} % Changed font size to 12pt
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} % Kept 1-inch margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\Large\bfseries}{\thesection}{0.5em}{}[\titlerule] % Increased section header size
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}
\titlespacing*{\section}{0pt}{2.0ex plus .1ex minus .2ex}{0.1in plus 1pt minus 1pt} % Adjusted space AFTER section titles/rules to 0.1in
\titlespacing*{\subsection}{0pt}{0.2in plus 2pt minus 1pt}{0.8ex plus .1ex} % Increased space BEFORE subsection titles to at least 0.2in

% Adjust paragraph spacing
\setlength{\parskip}{0.75em} % Kept at 75% of current font size (now 12pt)
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize and set indentation
\setlist[itemize]{nosep, leftmargin=0.5in} % Indent itemize lists by 0.50 inches

% Remove page number
\pagestyle{empty}

\begin{document}
      \begin{center} % Center-justify content
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Community-Driven in Kalamazoo, Michigan \\
      \mbox{\href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \&
            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}\\
      \href{tel:360-951-0354}{360-951-0354}

\end{center}

\section{Summary }
\noindent
Resourceful communications professional with over 15 years of experience developing and distributing compelling content to tell engaging stories for digital and print media. Proven ability to manage multi-channel communications to engage diverse communities, with a passion for supporting educational and youth-focused programs. Excels at collaborating with stakeholders to create materials that align with brand identity and organizational goals. Proficient in Adobe Creative Suite, content creation, and marketing material production.

\section{Skills}
\textbf{Languages {$\parallel$}} \small{{ French (Intermediate), English }}

\textbf{Tools and Technologies {$\parallel$}} \small{{ Adobe Creative Suite (Photoshop, InDesign, Illustrator), Canva, Microsoft Suite, MailChimp, WordPress, Social Media Platforms (Facebook, Twitter/X, LinkedIn)}}

\textbf{Proficiencies {$\parallel$}} \small{{ Content Creation, Digital \& Print Media, Marketing Materials Production, Newsletter \& Email Campaigns, Social Media Content Strategy, Storytelling, Stakeholder Engagement, Report Writing, Event Support, Branding \& Identity, Public Speaking, Collaboration, Project Management, Photography, Video Editing }}

\textbf{Educational Engagement {$\parallel$}} \small{{ Passionate about youth development, with experience as a YMCA summer camp teacher and college tutor; knowledgeable in Early Childhood Education and inclusive Special Education programs.}}

\section{Experience}
\subsection{\small{ Air Zoo Aviation Museum {$\parallel$} {Guest Experience Ambassador} \hfill \textbf{Aug 2024 - Current}}}
\begin{itemize}
    \item Applies childhood education training to engage children with science concepts using the museum’s Discovery Cart.
    \item Gathers and analyzes membership data to prepare reports for donors, highlighting community impact.
    \item Provides photography for internal training documents.
    \item Delivers interactive experiences to diverse audiences to enhance visitor engagement.
    \item Applies conflict resolution and active listening skills to address guest concerns and foster a welcoming environment.
\end{itemize}
\subsection{Communitrix, Remote {$\parallel$}{ Founder} \hfill
      \textbf{Sep 2023 – Current}}
\begin{itemize}
      \item Provides full-service community management for a diverse client base, designing and distributing marketing materials including newsletters, email campaigns, and social media content using MailChimp and WordPress.
      \item Develops and manages content strategies for multiple social media platforms to increase community engagement and brand visibility.
      \item Writes, edits, and curates compelling content for web and print, ensuring alignment with client brand identity.
      \item Establishes and maintains a small but strong client base, creating standard and milestone-based contracts to ensure clear deliverables and project success.
      \item Collaborates with clients to gather stories and information for use in promotional materials, fostering strong professional relationships.
\end{itemize}

\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June 2023}}
\begin{itemize}
      \item Produced and managed content for professional communities, including creating newsletters, reports, and social media updates.
      \item Wrote and edited copy for email campaigns, websites, and community forums, increasing community outreach activity from 2\% to 7\%.
      \item Coordinated with cross-functional teams in a fully remote environment to ensure consistent brand messaging.
      \item Organized and promoted virtual and in-person events to foster community engagement and build strong professional networks.
      \item Generated growth goals based on KPIs, using qualitative and quantitative member data to inform strategy and decision-making.

\end{itemize}
\subsection{\small{Internet Brands, El Segundo, CA {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2013 – July 2019}}}
\begin{itemize}
      \item Created and managed content for Model Mayhem across various digital platforms, including social media, newsletters, and educational blog posts, as well as for printed magazines.
      \item Implemented strategic social media campaigns that increased user engagement and brand visibility, improving moderator productivity and customer satisfaction from 61\% to 96\% year-over-year.
      \item Wrote and edited press releases and other marketing materials for distribution, ensuring consistent application of brand and visual identity.
      \item Built strong, lasting professional relationships with a distributed engineering team in Mexico, fostering effective cross-cultural collaboration.
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$} {Junior Developer} \hfill
      \textbf{Feb 2024 – June 2024}}
\begin{itemize}
      \item Top-ranking graduate of the online full-time full-stack web development bootcamp.
      \item Acted as project manager, implementing tickets, pull requests, and continuous integration testing using GitHub.
\end{itemize}

\subsection{University of Washington, Seattle {$\parallel$}{ Bachelor of Arts in Anthropology} \hfill
      \textbf{2011}}
\begin{itemize}
      \item Top-ranking graduate, Summa cum laude
      \item Completed coursework in communication, research, data analysis, and community development.
\end{itemize}

\end{document}