\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.1em} 
\setlength{\parindent}{0em} 

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Kalamazoo, MI $\parallel$ (360) 951-0354 $\parallel$ \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} $\parallel$ \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\paragraph{Relationship-driven and operationally-focused Corporate Account Manager with 7+ years of experience maximizing client retention, driving SaaS platform adoption, and building deep stakeholder rapport across diverse industries. Exceptional communicator skilled at distilling complex technical concepts into clear business value, managing contract renewals, and capturing user feedback to guide cross-functional product strategy.}

\subsubsection{\underline{Core Competencies}}

\begin{itemize}
    \item \textbf{Account Management \& Retention:} Strategic account health tracking, executive stakeholder alignment, churn mitigation, renewal discussions, proactive client outreach, relationship forecasting.
    \item \textbf{Client Engagement \& Adoption:} Onboarding playbook design, user training delivery, data-driven business reviews, white-space identification, value story collection, cross-functional sales support.
    \item \textbf{SaaS Operations \& Logic:} Advanced data reporting, process optimization, workflow auditing, custom automation (Google Apps Script), system logic troubleshooting, Agile frameworks.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Customer Success \& Operations Consultant} $\parallel$ \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Consult for client networks to optimize platform adoption, constructing centralized user knowledge bases, onboarding FAQs, and detailed operational documentation.
      \item Diagnose and resolve complex software environment configurations for corporate users by applying systematic, logical troubleshooting pipelines.
      \item Utilize generative AI tools and custom logic to accelerate administrative reporting, track client success metrics, and deliver polished analytics to executive stakeholders.
\end{itemize}
\vspace{1.5mm}
{\textbf{Account Manager \& Customer Success Specialist} $\parallel$ \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Managed end-to-end relationship health and contract renewals for high-profile corporate client accounts, successfully driving platform engagement from 2\% up to 7\%.
      \item Acted as the primary point of contact for inbound queries and outbound relationship campaigns, ensuring a highly professional, consultative experience.
      \item Programmed custom Google Apps Scripts to automate client reporting workflows, streamline routine data collation, and ingest clean user feedback loops.
      \item Partnered with account executives to identify account expansion opportunities, providing deep insights on user roles, metrics, and prospective user white space.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Success Specialist \& UX Liaison} $\parallel$ \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Administered high-volume user environments, boosting overall customer satisfaction from 61\% to 96\% through proactive outreach, user tutorials, and rapid escalation management.
      \item Extracted deep product feedback and value stories from active clients, circulating insights internally to sales, marketing, and engineering teams to refine business strategy.
      \item Authored internal procedural checklists and public-facing platform documentation to improve client onboarding efficiency and ensure consistent SLA compliance.
\end{itemize}
\vspace{1.5mm}
{\textbf{Client Relations Coordinator} $\parallel$ \textit{Breaktime Studios,}  \textbf{Remote} \hfill {Jan 2013 – July 2013}}
\begin{itemize}
      \item Managed live-ops client feedback pipelines for digital application environments, ensuring rapid communication triage between users and internal technical teams.
      \item Aggregated and structured software performance metrics and client feature requests to help support business cases for expansion and platform development.
\end{itemize}

\subsubsection{\underline{Technical Projects \& Software Logic Exposure}}

{\textbf{Project Manager \& Team Lead} $\parallel$ \textit{Fullstack Academy Capstone Project} \hfill {June 2024}}
\begin{itemize}
      \item Led a 4-person development pod, governing project milestones, task delegation, and deployment quality under an active Agile/Kanban workflow.
      \item Conducted extensive user play-testing blocks to capture user feedback, systematically analyzing friction points to optimize system usability and adoption.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} $\parallel$ Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} $\parallel$ Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}