\documentclass[a4paper,11pt]{article} % Changed font size to 11pt
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} % Reverted to 1-inch margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\Large\bfseries}{\thesection}{0.5em}{}[\titlerule] % Increased section header size
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}
\titlespacing*{\section}{0pt}{2.0ex plus .1ex minus .2ex}{0.1in plus 1pt minus 1pt} % Reverted space AFTER section
\titlespacing*{\subsection}{0pt}{0.2in plus 2pt minus 1pt}{0.8ex plus .1ex} % Reverted space BEFORE subsection

% Adjust paragraph spacing
\setlength{\parskip}{0.75em} % Reverted from 0.5em
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize and set indentation
\setlist[itemize]{nosep, leftmargin=0.5in} % Reverted indent from 0.25in

% Remove page number
\pagestyle{empty}

\begin{document}
      \begin{center} % Center-justify content
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Community-Driven in Kalamazoo, Michigan \\
      \mbox{\href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \&
            \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}}\\
      \href{tel:360-951-0354}{360-951-0354}

\end{center}

\section{Summary }
\noindent
Resourceful community-focused professional with a proven track record of activating communities, both digital and place-based. Excels at transforming challenges into opportunities for connection by facilitating dialogue, organizing engaging events, and demystifying complex processes for stakeholders.

\section{Skills}
\textbf{Languages {$\parallel$}} \small{{ French (Intermediate), JavaScript, SQL, LaTeX }} % \small is relative to 12pt

\textbf{Tools and Technologies {$\parallel$}} \small{{ GIS, Adobe Creative Suite (Photoshop, InDesign, Illustrator), Microsoft Suite, Canva, Miro, Figma, HubSpot CRM, Jira, Git, HTML, CSS }} % \small is relative to 12pt

\textbf{Proficiencies {$\parallel$}} \small{{ Community Organizing, Public Engagement, Event Facilitation, Report Writing, Data Analysis, Community Support, Conflict Resolution, Public Speaking, Project Management }} % \small is relative to 12pt
\section{Experience}
\subsection{\small{ Air Zoo Aviation Museum {$\parallel$} {Guest Experience Ambassador} \hfill \textbf{Aug 2024 - Current}}}
\begin{itemize}
      \item Facilitates educational programs and engages with guests to support the museum’s community outreach.
      \item Prepares membership data reports and supports programmatic improvements through stakeholder coordination.
\end{itemize}
\subsection{Communitrix, Remote {$\parallel$}{ Founder} \hfill
      \textbf{Sep 2023 – Current}}
\begin{itemize}
      \item Develops and implements community management plans for a diverse client base.
      \item Creates engagement strategies and provides ongoing support to build and sustain online communities.
\end{itemize}
\subsection{Community.co, Remote {$\parallel$}{ Community Manager} \hfill
      \textbf{July 2019 – June 2023}}
\begin{itemize}
      \item Managed and grew professional communities by facilitating engagement and coordinating virtual and in-person events.
      \item Prepared weekly reports on community trends and provided mentorship to team members.
\end{itemize}

\section{Education}
\subsection{Fullstack Academy, Remote {$\parallel$} {Junior Developer} \hfill
      \textbf{Feb 2024 – June 2024}}
\begin{itemize}
      \item Top-ranking graduate of an immersive full-stack web development bootcamp.
      \item Acted as project manager, implementing tickets, pull requests, and continuous integration testing.
\end{itemize}

\subsection{University of Washington, Seattle {$\parallel$}{ Bachelor of Arts in Anthropology}}
\begin{itemize}
      \item Top-ranking graduate, Summa cum laude.
      \item Coursework focused on community development, data analysis, and public engagement.
\end{itemize}

\end{document}