\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\bfseries}{\thesection}{0.1em}{}[\titlerule]
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.1em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.1em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.1em} 
\setlength{\parindent}{0em} 

% Reduce spacing in itemize
\setlist{nosep, leftmargin=*}

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
      {\LARGE \textbf{Hannah R. Johnson}} \\
      Kalamazoo, MI $\parallel$ (360) 951-0354 $\parallel$ \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} $\parallel$ \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

\paragraph{Hands on Customer Support Operations Leader with 7+ years of experience managing support teams, building automated routing logic, and optimizing ticketing workflows to drastically reduce response times. Exceptional aptitude for rapidly mastering new technical systems, with a proven history of designing standards, help center content, engineering custom automation scripts, and driving team accountability.}

\subsubsection{\underline{Core Competencies}}

\begin{itemize}
    \item \textbf{Support Operations \& Workflow Optimization:} Ticketing queue routing, response time reduction, backlog triage, macro design, help center content strategy, custom reporting dashboards, SLA compliance.
    \item \textbf{Team Leadership \& Accountability:} Managing 10+ agent support pods, agent productivity tracking, QA scorecards, onboarding checklist design, SOP creation, training program delivery, escalation handling.
    \item \textbf{Technical Logic \& Automation:} Rapid software system adoption, generative AI configuration, API logic, webhook workflows, script based reporting automation (Google Apps Script), data analysis.
\end{itemize}

\subsubsection{\underline{Professional Experience}}
{\textbf{Customer Support Operations Consultant} $\parallel$ \textit{Communitrix,}  \textbf{Remote} \hfill {Sep 2023 – Present}}
\begin{itemize}
      \item Consult for client networks to build centralized help center structures, comprehensive onboarding FAQs, and detailed standard operating procedures.
      \item Deploy and optimize generative AI tools and custom conversation logic to accelerate ticket resolution times, reduce manual agent backlogs, and streamline support routing.
      \item Analyze complex system outputs and telemetry data to design intuitive client facing workflows and deliver clean performance dashboards to executive stakeholders.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Success \& Support Operations Manager} $\parallel$ \textit{Community.co,}  \textbf{Remote} \hfill {July 2019 – June 2023}}
\begin{itemize}
      \item Headed support workflows and relationship health for high profile corporate networks, driving active platform engagement and ticket metrics from 2\% to a robust 7\%.
      \item Programmed custom Google Apps Scripts to automate administrative reporting, optimize data collation, and build automated communication loops.
      \item Managed queue routing rules, tags, and inbound triage paths to ensure consistent accountability, rapid resolution times, and seamless client escalation handling.
      \item Partnered directly with internal engineering squads to isolate active software bug logs, optimize data integrations, and accelerate feature delivery times.
\end{itemize}
\vspace{1.5mm}
{\textbf{Customer Support Specialist \& UX Liaison} $\parallel$ \textit{Internet Brands,}  \textbf{Remote} \hfill {July 2013 – July 2019}}
\begin{itemize}
      \item Administered high volume user ticketing queues across chat, email, and phone, scaling overall customer satisfaction (CSAT) metrics from 61\% to 96\% through systematic process overhauls.
      \item Authored rigorous internal training checklists and public facing platform documentation from scratch to accelerate agent onboarding and ensure strict SLA compliance.
      \item Extracted deep technical platform bugs and recurring user friction stories, translating findings into actionable feature briefs for product development and engineering teams.
\end{itemize}

\subsubsection{\underline{Technical Projects \& Team Leadership}}

{\textbf{Project Manager \& Technical Pod Lead} $\parallel$ \textit{Fullstack Academy Capstone} \hfill {June 2024}}
\begin{itemize}
      \item Directed an active software development pod through rigorous project milestones, managing daily stand ups, task delegation, and deployment schedules.
      \item Structured system testing blocks to capture user feedback, systematically analyzing bottlenecks to optimize system configuration and operational performance.
\end{itemize}

\subsubsection{\underline{Education \& Credentials}}
\textbf{Fullstack Academy} $\parallel$ Graduate, Full-Stack Web Development Bootcamp \hfill \textbf{2024} \\
\textbf{University of Washington} $\parallel$ Bachelor of Arts, Summa cum laude \hfill \textbf{2011}

\end{document}