% filepath: /home/icklekins/documents/resumeCM.tex
\documentclass[a4paper,12pt]{article} % Changed font size to 12pt
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} % Kept 1-inch margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

% Remove numbering from headings
\setcounter{secnumdepth}{0}

% Set up hyperref package
\hypersetup{
      colorlinks=true,
      urlcolor=black,
      linkcolor=black,
      citecolor=black,
      filecolor=black,
      menucolor=black,
      runcolor=black
}

% Define custom section format
\titleformat{\section}[hang]{\Large\bfseries}{\thesection}{0.5em}{}[\titlerule] % Increased section header size
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}[hang]{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}
\titlespacing*{\section}{0pt}{2.0ex plus .1ex minus .2ex}{0.1in plus 1pt minus 1pt} % Adjusted space AFTER section titles/rules to 0.1in
\titlespacing*{\subsection}{0pt}{0.2in plus 2pt minus 1pt}{0.8ex plus .1ex} % Increased space BEFORE subsection titles to at least 0.2in

% Adjust paragraph spacing
\setlength{\parskip}{0.75em} % Kept at 75% of current font size (now 12pt)
\setlength{\parindent}{0em} % No paragraph indentation

% Reduce spacing in itemize and set indentation
\setlist[itemize]{nosep, leftmargin=0.5in} % Indent itemize lists by 0.50 inches

% Remove page number
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hannah R. Johnson}} \\
    \vspace{1mm}
    Kalamazoo, MI \textbar{} \href{mailto:find.serendipity@gmail.com}{find.serendipity@gmail.com} \textbar{} \href{tel:360-951-0354}{360-951-0354} \textbar{} \href{https://www.linkedin.com/in/findserendipity/}{linkedin.com/in/findserendipity}
\end{center}

% --- SUMMARY ---
\section{Summary}
Senior Global Community Manager with over 15 years of experience building, engaging, and supporting vibrant online communities, including extensive work in the gaming industry. A unique hybrid professional who combines deep community strategy with hands-on technical skills in static website development (HTML, CSS, JavaScript), maintenance, and security. Proven ability to drive player engagement through compelling content, data-driven communication strategies, and a passion for creating positive, inclusive digital spaces.

% --- SKILLS ---
\section{Core Competencies}
\begin{itemize}
    \item \textbf{Community Strategy:} Global Community Management, Player Engagement \& Retention, Content Strategy, Moderation, Social Media Management, Brand Ambassadorship, Analytics \& Reporting
    \item \textbf{Web Development:} Static Website Development (HTML, CSS, JavaScript), Website Maintenance \& Security, Bug Troubleshooting, SEO Principles, Performance Optimization
    \item \textbf{Tools \& Platforms:} Google Suite (Drive, Docs, Sheets), Adobe Creative Suite (Photoshop, Illustrator), WordPress, MailChimp, Jira, Git, Various CMS \& Forum Platforms
\end{itemize}

% --- EXPERIENCE ---
\section{Professional Experience}

\subsection{Founder, Community \& Web Development Consultant \hfill Sep 2023 – Present}
\textit{Communitrix, Remote}
\begin{itemize}
    \item Develop, maintain, and optimize static websites for a diverse client base, utilizing HTML, CSS, and JavaScript to build features and ensure cross-browser compatibility.
    \item Troubleshoot technical issues, resolve bugs, and implement security patches to ensure high uptime and website stability.
    \item Create and integrate visual assets such as graphics, banners, and icons to enhance branding and community engagement.
    \item Manage client community channels, including forums and social media, and develop player communication strategies through email newsletters and platform announcements.
\end{itemize}

\subsection{Community Manager \hfill July 2019 – June 2023}
\textit{Community.co, Remote}
\begin{itemize}
    \item Managed a portfolio of high-profile professional communities for major publications including Forbes, Fast Company, and Rolling Stone Culture Council.
    \item Produced and managed content for newsletters, reports, and social media updates, driving community growth and engagement.
    \item Coordinated with cross-functional technical teams to ensure consistent brand messaging and support website updates.
    \item Generated growth goals based on KPIs, using qualitative and quantitative member data to inform strategy.
\end{itemize}

\subsection{Community \& Customer Service Manager \hfill July 2013 – July 2019}
\textit{Internet Brands / Model Mayhem, El Segundo, CA}
\begin{itemize}
    \item Created and managed content across digital platforms, including social media, newsletters, and educational blog posts.
    \item Implemented strategic social media campaigns that increased user engagement and brand visibility, improving moderator productivity and customer satisfaction from 61\% to 96\% year-over-year.
    \item Wrote and edited press releases and other marketing materials, ensuring consistent application of brand identity.
\end{itemize}

\subsection{Community Manager, Gaming \hfill Jan 2013 – July 2013}
\textit{Breaktime Studios, Remote}
\begin{itemize}
    \item Simultaneously managed communities for a portfolio of eight mobile game titles.
    \item Created engaging multimedia content for social media, resulting in a 50\% growth in Facebook following through targeted campaigns.
    \item Acted as the primary liaison between the player base and development teams, communicating feedback and reporting on community sentiment.
\end{itemize}

\subsection{Social Media Strategist \& Community Moderator \hfill 2009 – 2013}
\textit{Metaverse Mod Squad \& Zynga Games, Remote}
\begin{itemize}
    \item Built and maintained brand pages for diverse clients on Facebook, Twitter, and WordPress at Metaverse Mod Squad.
    \item Provided community moderation and social media support for multiple iPhone games at Zynga.
    \item Authored weekly reports on community trends using data-driven models and created game guides to support player retention.
\end{itemize}

% --- EDUCATION & TECHNICAL TRAINING ---
\section{Education \& Technical Training}
\subsection{Fullstack Academy, Remote \hfill 2024}
\textit{Top-Ranking Graduate, Full-Stack Web Development Bootcamp}
\begin{itemize}
    \item Completed an immersive program focused on modern web technologies, including JavaScript, React, and Node.js.
    \item Acted as project manager for capstone projects, implementing tickets, pull requests, and CI testing using GitHub.
\end{itemize}

\subsection{University of Washington, Seattle \hfill}
\textit{Bachelor of Arts in Anthropology, Summa cum laude}

\end{document}